---
title: "Exploration 13"
author: "Jack, James, and Zach"
date: "`r format(Sys.time(), '%d %B, %Y')`"
header-includes: \usepackage{dcolumn}
output: pdf_document
---
```{r include=FALSE, cache=FALSE}
# Some customization.  You can alter or delete as desired (if you know what you are doing).
# knitr settings to control how R chunks work.

## To make the html file do
## render("exploration4.Rmd",output_format=html_document(fig_retina=FALSE))
## To make the pdf file do
## render("exploration4.Rmd",output_format=pdf_document())

require(knitr)
opts_chunk$set(
  tidy=FALSE,     # display code as typed
  echo=TRUE,
  results='markup',
  strip.white=TRUE,
  fig.path='figs/fig',
  cache=FALSE,
  highlight=TRUE,
  width.cutoff=132,
  size='footnotesize',
  out.width='.9\\textwidth',
  fig.retina=FALSE,
  message=FALSE,
  comment=NA)

if(!file.exists('figs')) dir.create('figs')

options(SweaveHooks=list(fig=function(){
			   par(mar=c(3.5, 3, 1.1, 0),
			       pty="s",
			       mgp=c(1.5,0.5,0),
			       oma=c(0,0,0,0))},
			 echo=function(){options(continue=" ") ##Don't show "+" prompts,
			 options(prompt=" ")
			 }),
	digits=4,
	scipen=8,
	width=132
	)
options(error=function(){options(prompt="> ",continue="+ ");NULL})
```

```{r setup, include=FALSE}
library(readstata13)
library(tidyverse)
library(car)
library(bayesplot)
library(rstanarm)
library(ggplot2)
library(stargazer)

##summary(anes16$V162313) #feeling thermometer toward illegal immigrants
##summary(anes16$V162034a) #who did R vote for for pres? 2=Trump
anes16 <- read.dta13("http://jakebowers.org/PS531/anes_timeseries_2016.dta")
anes16$income <- ifelse(anes16$V161361x<1,NA,anes16$V161361x)
anes16$state <- anes16$V163001b
anes16$gender <- factor(ifelse(anes16$V161342 == -9, NA, ifelse(anes16$V161342 == 3, NA, anes16$V161342)))
anes16$immigrantPost = ifelse(anes16$V162313 < 0, NA, anes16$V162313)
anes16$pid <- factor(with(anes16,ifelse( V161158x<0,NA,V161158x )))
anes16$educyrs <- with(anes16,ifelse(V161270<0 | V161270 %in% c(90,95),NA,V161270-1))
anes16$ftTrumpPost <- with(anes16, ifelse(V162079 < 0 | V162079 == 998, NA, V162079))
anes16$age <- with(anes16,ifelse(V161267<0,NA,V161267))
anes16$ftTrumpPre <- with(anes16, ifelse(V161087 < 0 | V161087 == 998, NA, V161087))
anes16$immigrantPre = ifelse(anes16$V161192 < 0, NA, anes16$V161192)

anes16$state = as.factor(anes16$state)
anes16$pid = as.numeric(anes16$pid)
anes16$gender <- factor(ifelse(anes16$V161342 == -9, NA, ifelse(anes16$V161342 == 3, NA, anes16$V161342)))

covs <- c("educyrs","age","gender","pid","income","state", "immigrantPost", "ftTrumpPost", "ftTrumpPre", "immigrantPre")
nes16 <-  anes16[,covs]



nes16a = nes16[, - 5]
nes16a = na.omit(nes16a)

nes16b = nes16[, - 7]
nes16b = na.omit(nes16b)

nes16c = nes16[, -c(1:5)]
nes16c = na.omit(nes16c)

output = stan_glm(ftTrumpPost~immigrantPost + educyrs + age + gender + pid, data = nes16)
output2 = stan_glm(ftTrumpPost~income + educyrs + age + gender + pid, data = nes16)
output3 = stan_glm(ftTrumpPre~immigrantPre + educyrs + age + gender + pid, data = nes16)
output4 = stan_glm(ftTrumpPre~income + educyrs + age + gender + pid, data = nes16)
```
So after cleaning up the data a little bit more than you did (thanks!), we ran some models predicting the Trump vote[on a feeling thermometer] by pre-election immigration status toward unauthorized immigrants [feeling thermometer] and respondents' income. We also ran some models with post-election income of respondents and post election answers to a question about illegal immigration.

```{r, echo=FALSE, results='asis'}
stargazer(output, output2, header = F)
```
#As far as answering the question of whether SES of immigration does a better job predicting the Trump vote, our models suggest that immigration does a slightly better job than income--which we chose as a proxy for SES. 

```{r, echo=FALSE}
par(mfrow = c(2,2))
plot(output3)#pre imm
plot(output4)#pre inc
plot(output)
plot(output2)
```

```{r}
prior_summary(output3)
my_prior=normal(location=0,scale=10,autoscale = F)

Imm_1 <- stan_glm(ftTrumpPost ~ V162313 + income+educyrs + age + gender + pid, data=anes16, chains = 4, seed = 12345)
summary(Imm_1 )
plot(Imm_1)

Imm_2 <- stan_glm(ftTrumpPost ~ V162313 + income+educyrs + age + gender + pid, data=anes16, chains = 4,prior=my_prior, seed = 12345)
summary(Imm_2 )
plot(Imm_2)

Imm_1$coefficients
Imm_2$coefficients
```
Our plan was to use the pre-election models as our prior information to inform the models of post-election feeling thermometer scores toward Trump; however, we were having some trouble specifying the pre-election models as prior information.

We are pretty sure that the prior distribution we specified isn't correct as the prior information didn't improve our predictions much at all. We would expect that pre-election information would be highly informative, not weakly informative. Hence, this is why we think that we specified the priors incorrectly. 

